Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-09-06 paper.tex
corrected Brown+ 2011 citation

This exponential dependence of radio halo luminosity with turbulence then raises
the interesting question of why radio halo scaling relations (e.g.,
$L_{\nu}$--$L_{\rm X}$) are so tight. Previous statistical modelling of radio
halo populations \citep{2006MNRAS.369.1577C,2007MNRAS.378.1565C} have focused
on matching the mean relations, but not the scatter. We believe the latter
provides a particularly interesting and potentially fruitful constraint. The
acceleration timescale $\tau_{\rm D}$ and the length of time during which
acceleration takes place $\tau_{\rm cl}$ must be matched so that there are
roughly $\sim 2$ e-folds (given the factor $\sim 10$ difference in radio
luminosity between the radio bright and faint populations; \citet{brown11}),
otherwise scatter in turbulence (which we might expect given the wide variety of
merger and infall conditions) will be exponentially amplified in radio
luminosity. The timescale of the merger has some natural scatter which is not
obviously correlated with $\tau_{\rm D}$.

>>>>

This exponential dependence of radio halo luminosity with turbulence then raises
the interesting question of why radio halo scaling relations (e.g.,
$L_{\nu}$--$L_{\rm X}$) are so tight. Previous statistical modelling of radio
halo populations \citep{2006MNRAS.369.1577C,2007MNRAS.378.1565C} have focused on
matching the mean relations, but not the scatter. We believe the latter provides
a particularly interesting and potentially fruitful constraint. The acceleration
timescale $\tau_{\rm D}$ and the length of time during which acceleration takes
place $\tau_{\rm cl}$ must be matched so that there are roughly $\sim 2$ e-folds
(given the factor $\sim 10$ difference in radio luminosity between the radio
bright and faint populations; \citealt{2011ApJ...740L..28B}), otherwise scatter
in turbulence (which we might expect given the wide variety of merger and infall
conditions) will be exponentially amplified in radio luminosity. The timescale
of the merger has some natural scatter which is not obviously correlated with
$\tau_{\rm D}$.
